---
title: "fourc"
author: "Nathan Harmston"
date: "13 February 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(affy)
library(simpleaffy)
library(affy)
library(affxparser)
library(GenomicRanges)
library(preprocessCore)
library(rtracklayer)
```

```{r eval=FALSE}
https://github.com/benja0x40/MiMB.4C
library("devtools")
install_github("benja0x40/MRA.TA")

Rscript computeRestrictionMap.R -n DpnII  -m GATC -s genomes/UCSC_mm9/genome.fa.gz -i mm9 -r Processed_Data/mm9_restriction_map
```

```{r}
library("MRA.TA")
covdata = read.delim("covdata.txt")

map.mm8 = read.delim("GPL14183_PRNFGMm2b520462F_rev.txt")
bpmap_file =  "GPL14183_PRNFGMm2b520462F_rev.bpmap"
bpmap <- readBpmap(bpmap_file)
summary(bpmap)

cel_files <- list.files("./",".CEL$")

cel_header <- readCelHeader(cel_files[1])
cel_indices <- lapply(bpmap, function(x) xy2indices(x[["pmx"]],  
x[["pmy"]], nc=cel_header[["cols"]]))
```

Import coordinates of restriction fragments and match with probe coordinates
-----------------------------------------------------------------------------.
Read precomputed restriction fragments
```{r}
fragments <- readData( "mm9_DpnII_Fragments.txt.gz",
  file.formats$restriction.fragment
)

# Define restriction fragments’ start and end (which depends on the enzyme)
fr.len <- with(fragments, RS3.START - RS5.END + 1)
fr.start <- fragments$RS5.END
fr.end <- fragments$RS3.START

# Make genomic intervals with probe and restriction fragment coordinates

mm8.locations <- GRanges("chr2", IRanges(bpmap[["Mm:NCBIv36;chr2"]]$startpos, width=nchar(bpmap[["Mm:NCBIv36;chr2"]]$probeseq)), strand="*")

ch.two = import.chain("mm8ToMm9.over.chain")
results = liftOver(mm8.locations, ch.two)

probes.grg = do.call(c, results)

fragments.grg <- GRanges(
  seqnames=as.character(fragments$CHR),
  ranges=IRanges(
    start=fr.start, end=fr.end,
    names=as.character(fragments$RFID)
  )
)

# Match probes to fragments using respective genomic intervals
probes.grg <- matchProbesToFragments(probes.grg, fragments.grg)
```

Rerun with different values of tissue and bait to generate all required datasets

```{r}
tissue = "limb"
bait = "d4"
data <- readCelIntensities(as.character(covdata$FileName[covdata$Tissue==tissue & covdata$Bait==bait]), cel_indices[["Mm:NCBIv36;chr2"]])

# Match array data to updated design using probe identifiers
r1.4C <- data[,1]
r1.ct <- data[,3]
r2.4C <- data[,2]
r2.ct <- data[,4]
```

Normalization procedure
-----------------------------------------------------------------------------.
Compute raw A and M values in each replicate

```{r}
r1.A <- (log2(r1.4C) + log2(r1.ct))/2 # average
r1.M <- (log2(r1.4C) - log2(r1.ct))   # log2 ratio
r2.A <- (log2(r2.4C) + log2(r2.ct))/2 # average
r2.M <- (log2(r2.4C) - log2(r2.ct))   # log2 ratio
```

Normalization procedure (Step by step alternative)
-----------------------------------------------------------------------------.
# Apply background bias correction and lowess normalization to each replicate
```{r}
  # Compute raw A and M values in each replicate
  r1.A <- (log2(r1.4C) + log2(r1.ct))/2
  r1.M <- (log2(r1.4C) - log2(r1.ct))
  r2.A <- (log2(r2.4C) + log2(r2.ct))/2
  r2.M <- (log2(r2.4C) - log2(r2.ct))
  
  bb.r1 <- backgroundBiasEstimation(r1.A, r1.M, plots = T)
  bb.r2 <- backgroundBiasEstimation(r2.A, r2.M, plots = T)

  res <- backgroundBiasCorrection(r1.A, r1.M, theta=bb.r1)
  r1.A <- res$x; r1.M <- res$y
  res <- backgroundBiasCorrection(r2.A, r2.M, theta=bb.r2)
  r2.A <- res$x; r2.M <- res$y

  res <- lowessCorrection(r1.A, r1.M, lowess.f=0.2, plots = T)
  r1.A <- res$x; r1.M <- res$y
  res <- lowessCorrection(r2.A, r2.M, lowess.f=0.2, plots = T)
  r2.A <- res$x; r2.M <- res$y
```
Probe selection
-----------------------------------------------------------------------------.
Identify probes likely associated with best/problematic signals with raw data
```{r}
r1.EQ <- enrichmentQuality(r1.ct, r1.4C, plots=T) # Replicate 1
r2.EQ <- enrichmentQuality(r2.ct, r2.4C, plots=T) # Replicate 2
```


Make control plot of normalized 4C signal versus probe distance to site
```{r}
plotProbeDistanceControls(r1.M, rnk=probes.grg$RF_RANK, dis=probes.grg$RF_DIST, dlim=c(-1500, 1500), QF=r1.EQ)
plotProbeDistanceControls(r2.M, rnk=probes.grg$RF_RANK, dis=probes.grg$RF_DIST, dlim=c(-1500, 1500), QF=r2.EQ)
```

Filtering option 1:
fragment too short OR no fragment assigned OR distance to site too large
```{r}
reject <- with(probes.grg, RF_LEN < 50 | is.na(RF_ID) | RF_DIST>250)
```

Filtering option 2:
Reject when fragment too short OR no fragment assigned OR rank to site too large
```{r}
#reject <- with(probes.grg, RF_LEN < 50 | is.na(RF_ID) | RF_RANK>2)
```

Always filter out probes associated to a problematic signal in both replicates
```{r}
reject <- reject | (r1.EQ$is.worst & r2.EQ$is.worst)
```

Make control plot of selected probes (4C signal versus probe distance to site)
```{r}
plotSelectedProbes(r1.A, r1.M, dis=probes.grg$RF_DIST, sel = ! reject)
plotSelectedProbes(r2.A, r2.M, dis=probes.grg$RF_DIST, sel = ! reject)
```

Update probes and normalized data to retain accepted probes only
```{r}
probes.grg <- probes.grg[! reject]
r1.A <- r1.A[! reject] # For consistency with r1.M and probes.grg
r1.M <- r1.M[! reject]
r2.A <- r2.A[! reject] # For consistency with r2.M and probes.grg
r2.M <- r2.M[! reject]
```

4C enrichement scores
-----------------------------------------------------------------------------.
Calculate the number of accepted probes per half-fragment (5’ and 3’ ends)
```{r}
probes.grg <- countProbesPerFragment(probes.grg) 
```

Average 4C enrichments in each half-fragment
```{r}
y1 <- combineByFragment(r1.M, probes.grg, FUN=mean) # Replicate 1
y2 <- combineByFragment(r2.M, probes.grg, FUN=mean) # Replicate 2
```
Compute statistical scores and pool replicates into combined 4C enrichment scores

```{r}
y1$SCORE <- enrichmentScore(y1$VALUE)
y2$SCORE <- enrichmentScore(y2$VALUE)

Yi <- y1$SCORE + y2$SCORE
Yi <- sapply(-2*Yi, pchisq, df=2*2, lower.tail=FALSE, log.p=FALSE)

fourc.grg = GRanges("chr2", IRanges(y1$SITE, width=1), strand="*", y1.value = y1$VALUE, y1.score = y1$SCORE,
                y2.value = y2$VALUE, y2.score = y2$SCORE,
                pvalue = Yi, fdr = p.adjust(Yi, "fdr"),
                logpvalue = -log10(Yi), logfdr = -log10(p.adjust(Yi, "fdr")), id=y1$RF_ID
        )
```

```{r}
saveRDS(fragments.grg, "GSE31659_fourc_fragments_grg.rds")

saveRDS(fourc.grg, paste("GSE31659_fourc", tissue, bait, "grg.rds", sep="_"))

```



```{r}
sessionInfo()
```
